\plaintitle

### 2017-06-07 papers/IoT2017/analysis.tex
no message

Second, we can show that the amount of energy bids (or asks) posted at the same time by prosumer $i$ for each timestep is at most $\field{MAXEPA}_i + \field{MAXECA}_i$.
Notice that the limit is higher than for net energy sold or bought, since prosumer $i$ may purchase $\field{MAXECA}_i$ amount of EPA (or $\field{MAXEPA}_i$ amount of ECA) from other prosumers, and then post an energy ask (or bid) in the amount of $\field{MAXEPA}_i + \field{MAXECA}_i$.

>>>>

Second, we can show that the total amount of energy bids (or asks) posted at the same time by prosumer $i$ for each timestep is at most $\field{MAXEPA}_i + \field{MAXECA}_i$.
Notice that the limit is higher than for net energy sold or bought, since prosumer $i$ may purchase $\field{MAXECA}_i$ amount of EPA (or $\field{MAXEPA}_i$ amount of ECA) from other prosumers, and then post an energy ask (or bid) in the amount of $\field{MAXEPA}_i + \field{MAXECA}_i$.

### 2017-06-07 papers/IoT2017/services.tex
no message

To prevent this, prosumers transfer assets to their anonymous addresses through a \emph{mixing service}. 
The mixing service prevents tracing the assets back to their original owners by mixing together multiple incoming transfers and multiple outgoing transfers, thereby hiding the connections between the prosumers and the anonymous addresses.
In practice, a mixing service can be implemented using multiple approaches.
The simplest one is to use a \emph{trusted third party}, called a cryptocurrency tumbler, which can receive and send assets.
However, anonymity in this case depends on the trustworthiness and reliability of the third party, who could easily de-anonymize the addresses.
A more secure approach is to used decentralized protocols, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
These protocols enable participants to mix assets with each other, thereby eliminating the need for a trusted third party, which would constitute a single point of failure.
Some newer cryptocurrencies, such as Zerocoin~\cite{miers2013zerocoin},  provide built-in mixing services, which are often based on cryptographic principles and proofs.

@@

The energy consumption balance $E_i^t$ of prosumer $i$ is
\begin{align*}
E_i^t = & \hphantom{+} \text{measured net energy consumption during timeslot } t \\ %\text{measured consumption} - \text{measured production} \\
 & - \sum_{epa \,\in\, \{\text{EPA deposited by } i\}: ~ epa.\field{start} \,\leq\, epa.\field{end}} epa.\field{power} \\
 & + \sum_{epa \,\in\, \{\text{EPA withdrawn by } i\}: ~ epa.\field{start} \,\leq\, epa.\field{end}} epa.\field{power} .
% & + \text{EPA deposited by $i$} - \text{EPA withdrawn by $i$} .
\end{align*}
Notice that consumption assets are not used directly for billing, they are only used to enforce security and safety requirements.

>>>>

To prevent this, prosumers transfer assets to their anonymous addresses through a \emph{mixing service}. 
The mixing service prevents tracing the assets back to their original owners by mixing together multiple incoming transfers and multiple outgoing transfers, thereby hiding the connections between the prosumers and the anonymous addresses.
In practice, a mixing service can be implemented using multiple approaches.
The simplest one is to use a \emph{trusted third party}, called a cryptocurrency tumbler, which can receive and send assets.
However, anonymity in this case depends on the trustworthiness and reliability of the third party, who could easily de-anonymize the addresses.
A more secure approach is to used decentralized protocols, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
These protocols enable participants to mix assets with each other, thereby eliminating the need for a trusted third party. %, which would constitute a single point of failure.
Some newer cryptocurrencies, such as Zerocoin~\cite{miers2013zerocoin},  provide built-in mixing services, which are often based on cryptographic principles and proofs.

@@

The energy consumption balance $E_i^t$ of prosumer $i$ is
\begin{align*}
E_i^t = & \hphantom{+} \text{measured net energy consumption during timeslot } t \\ %\text{measured consumption} - \text{measured production} \\
 & - \sum_{epa \,\in\, \{\text{EPA deposited by } i\}: ~ epa.\field{start} \,\leq\, t \,\leq\, epa.\field{end}} epa.\field{power} \\
 & + \sum_{epa \,\in\, \{\text{EPA withdrawn by } i\}: ~ epa.\field{start} \,\leq\, t \,\leq\, epa.\field{end}} epa.\field{power} .
% & + \text{EPA deposited by $i$} - \text{EPA withdrawn by $i$} .
\end{align*}
Notice that consumption assets are not used directly for billing, they are only used to enforce security and safety requirements.
